Methods that remove batch effects while retaining group differences may lead to exaggerated confidence in downstream analyses

### 2014-07-17 tex/manuscript.tex
Updated boxplot with ANOVA
Replaced ComBat centering with two-way ANOVA (using limma) in Figure 1.
Updated manuscript text accordingly.

\begin{figure}[!p]
\centering\includegraphics[width=13cm]{Fig/boxplots.pdf}
%\centering\includegraphics[width=13cm]{Fig/boxplots.png}
\caption{Simulated data from four study groups was generated where groups 1 and 2 have lower means than groups 3 and 4. These were placed in three different batches with batch effects added. Values and boxes showing group mean with 95\%~confidence intervals are displayed for data without batch effects, after adding batch effects, after batch centering, and after two-way ANOVA based batch centering. The last frame shows the least squares estimates of the group means from a two-way ANOVA. This case, design and effects, was selected to illustrate the spurious effects that may arise.
\NOTE{Replace ComBat with ANOVA in plot.}}
\label{fig:boxplots}
\end{figure}

>>>>

\begin{figure}[!p]
\centering\includegraphics[width=13cm]{Fig/boxplots.pdf}
%\centering\includegraphics[width=13cm]{Fig/boxplots.png}
\caption{Simulated data from four study groups was generated where groups 1 and 2 have lower means than groups 3 and 4. These were placed in three different batches with batch effects added. Values and boxes showing group mean with 95\%~confidence intervals are displayed for data without batch effects, after adding batch effects, after batch centering, and after two-way ANOVA based batch centering (using \texttt{limma}). The last frame shows the least squares estimates of the group means from a two-way ANOVA. This case, design and effects, was selected to illustrate the spurious effects that may arise.
}
\label{fig:boxplots}
\end{figure}
